Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-09-01 analysis/report/draft-manuscript.Rmd
update csl template; tweaks

---
title: "Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers"
output:
  word_document: default
  html_document: 
    keep_md: yes
  bookdown::html_document2:
    number_sections: false
    toc: false
bibliography: references.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ieee-transactions-on-medical-imaging.csl
link-citations: yes
zotero: true
---

@@

Figure 2 shows event rates by vaccine type, and the unadjusted incidence ratio ratio. Over the duration of `r   label_number(0.1)(baseline$fu_years)` person-years of follow-up there were `r baseline$postest` positive SARS-CoV-2 tests, `r baseline$covidadmitted` COVID-19 hospital admissions, and `r baseline$coviddeath` COVID-19 deaths.

@@

At 6 weeks post-vaccination, the absolute risk difference (ChAdOx1 - BNT162b2) for a positive SARS-CoV-2 test was `r filter(riskdifference, outcome=="postest", tstop==7*6)$diff_format` per 1000 people, and for COVID-19 hospital admissions was `r filter(riskdifference, outcome=="covidadmitted", tstop==7*6)$diff_format` per 1000 people.

>>>>

---
title: "Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers"
output:
  html_document: 
    keep_md: yes
  word_document: default
  bookdown::html_document2:
    number_sections: false
    toc: false
bibliography: references.bib
csl: nature.csl # from https://raw.githubusercontent.com/citation-style-language/styles/master/nature.csl
link-citations: yes
zotero: true
---

@@

Table 2 shows event rates by vaccine type, and the crude incidence. Over the duration of `r label_number(0.1)(baseline$fu_years)` person-years of follow-up there were `r baseline$postest` positive SARS-CoV-2 tests, `r baseline$emergency` A&E attendances, `r baseline$covidadmitted` COVID-19 hospital admissions, and `r baseline$coviddeath` COVID-19 deaths.

@@

At 6 weeks post-vaccination, the absolute risk difference (ChAdOx1 - BNT162b2) for a positive SARS-CoV-2 test was `r filter(riskdifference, outcome=="postest", tstop==7*6)$diff_format` per 1000 people, for A&E attendances was `r filter(riskdifference, outcome=="emergency", tstop==7*6)$diff_format` and for COVID-19 hospital admissions was `r filter(riskdifference, outcome=="covidadmitted", tstop==7*6)$diff_format` per 1000 people.
